\sectiontitle{work experience}
\sectioncontent{

  \job{Vidya Holdings Ltd., London, UK}{Software Engineer}{Oct 2021 - Now}
    \begin{itemize}
    \item Design software for the control of a high-throughput IVD (\textit{in vitro} diagnostics) medical device, which includes a Qt GUI, interfacing with external hardware, and image analysis units.
    \item Develop image analysis software and deploy it as a microservice on a remote Linux server using Kubernetes-orchestrated Docker containers. Interact with users and manage the job queue with FastAPI, Celery, and Redis.
    \item Work within a team of five in an Agile framework, using the Scrum methodology. Negotiate user stories with stakeholders, document the details in Jira, refine user stories, and estimate story points.
    \end{itemize}
  \spacevv

    \job{University of Cambridge}{Postdoctoral Research Associate}{Oct 2020 – Sep 2021}
    \begin{itemize}
    \item Analysed brain histology images to study rare dementia conditions such as progressive supranuclear palsy.
    \item Applied statistical learning with Bayesian inference to analyse the cellular features extracted from image data and associate them with clinical metadata. Created data report and visualisation using R, Python and Jupyter Notebook.
    \item Supervised a PhD student for their research project on machine learning of neuropathology image data.
    \end{itemize}
    \spacevv

    \job{University of Cambridge}{Research Student}{Oct 2016 - Sep 2020}
    \begin{itemize}
    \item Established a novel fluorescence imaging technique for protein aggregates associated with dementia.
    \item Created a mathematical model in MATLAB for simulating enzyme kinetics with machine learning approach.
    \item Developed multiple pieces of Python software for fluorescence image data acquisition and analysis. Expanded their capacity to suit for projects across the research group and provided user training.
    \end{itemize}
    \spacevv

    \job{University of Cambridge}{Laboratory Teaching Assistant}{Oct 2016 – Mar 2018}
    
    Supervised groups of 5 – 10 undergraduate students in practical and computational chemistry courses.
    \spacevv

    \job{Procter \& Gamble Ltd., Newcastle-upon-Tyne}{R\&D Intern}{Aug 2015 – June 2016}
    \begin{itemize}
    \item Worked in a team within the process department to improve the quality consistency of fragrance additives.
    \item Investigated the sources of variability for a quality control procedure using statistical analysis.
    \end{itemize}
    
}
